### 2014-09-11 paper/paper.Rmd
resized pisa image to fit better, tweaking code, language

```{r studying, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
student.luke <- student2012[,c("name","PV1MATH","PV1READ","PV1SCIE","ST57Q01")]
#study.luke <- melt(student.luke,id=c("name","ST57Q01"))
studyplot <- ggplot(data = student.luke, aes(ST57Q01, PV1MATH)) + facet_wrap(~name) + stat_smooth(se=F)
studyplot
```

@@

```{r studytime, warning = FALSE, message=FALSE, echo=FALSE}
.width = 1

data_small <- 
  student2012 %>%
  dplyr::select(OECD, name, OUTHOURS) %>%
  filter(!is.na(OUTHOURS))

ggplot(mapping = aes(x = OUTHOURS)) + 
  scale_x_continuous(name = "out of school study time (hours)", limits = c(0,60)) +
  scale_y_continuous(name = "density") +
  geom_histogram(
    mapping = aes(y = ..density.., fill = OECD), 
    binwidth = .width,
    data = data_small %>% filter(OECD == "Albania")
  ) + 
  scale_fill_manual(
    values = "black",
    breaks = "Albania",
    guide = guide_legend(title = "")
  ) + 
  geom_line(
    mapping = aes(group = name, color = OECD), 
    stat = "density", 
    alpha = 0.3,
    data = data_small %>% filter(OECD != "Albania")
  ) +
  scale_color_discrete(
    guide = guide_legend(
      title = "Other Countries",
      override.aes = list(alpha = 1)
    )

  ) +
  scale_colour_manual(values = c("#f4a582", "#92c5de")) + guides(colour = guide_legend(override.aes = list(alpha = 1)))
```

@@

shiny, plyr, dplyr, ggplot2

>>>>

```{r studying, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
student.luke <- student2012[,c("name","PV1MATH","PV1READ","PV1SCIE","ST57Q01")]
#study.luke <- melt(student.luke,id=c("name","ST57Q01"))
studyplot <- ggplot(data = student.luke, aes(ST57Q01, PV1MATH), xlab="Time spent", ylab="Math scores") + facet_wrap(~name) + stat_smooth(se=F)
studyplot
```

@@

@@

The following R packages were used to conduct the data exploration: shiny, plyr, dplyr, ggplot2, stringr, reshape2, lubridate, maps, ggmap, htmltools, rworldmap, grid, scales, doBy.
